Block bootstrap consistency\\under weak assumptions

### 2015-12-31 Paper.tex
[#16] Finish correct capitalization of De Jong
This capitalization issue was initially fixed when I updated the
remote submodule; this commit finishes it.

Closes #16

\documentclass[11pt]{article}
\input{preamble}

\begin{document}

\author{Gray Calhoun\thanks{Economics Department, Iowa State
    University, Ames, IA 50011. Telephone: (515) 294-6271.  Email:
    \protect\url{gcalhoun@iastate.edu}. Web:
    http://www.econ.iastate.edu/$\sim$gcalhoun.  I would like to thank
    Helle Bunzel, Dimitris Politis, Robert Taylor, and three anonymous
    referees for their comments and feedback on earlier versions of
    this paper.}}

@@

\begin{abstract}\noindent
  This paper weakens the size and moment conditions needed for typical
  block bootstrap methods (i.e.\ the Moving Blocks, Circular Blocks,
  and Stationary Bootstraps) to be valid for the sample mean of
  Near-Epoch-Dependent (\ned) functions of mixing processes; they are
  consistent under the weakest conditions that ensure the original
  \ned\ process obeys a Central Limit Theorem \citep[those
    of][\textit{Econometric Theory}]{Jon:97}.  In doing so, this paper
  extends de Jong's method of proof, a blocking argument, to hold with
  random and unequal block lengths.  This paper also proves that
  bootstrapped partial sums satisfy a Functional \clt\ under the same
  conditions.

@@

As mentioned earlier, these are the same size and mixing conditions
used by \citet{Jon:97}.
Note that de Jong does allow a little bit more flexibility in the
conditions on the array $\{c_{nt}\}$ \citep[see also][]{Dav:93};
essentially, he allows for a single set of blocks with the
maximal $\{c_{nt}\}$ over each block well-behaved, while this
paper requires this condition to hold for every possible partition of
blocks.  This additional restriction is required because the
Stationary Bootstrap will select the blocks randomly and is similar to
\citepos{JoD:00b} requirement for the \fclt. Similarly, our assumption
on the dispersion of the individual means, $(\mu_{nt} - \bar\mu_n)^2$, is
slightly stronger than \citepos{GoW:02} and \citepos{GoJ:03} to
accommodate larger block sizes.

@@

Results~\eqref{eq:32} and~\eqref{eq:33} are direct extensions of
\citepos{Jon:97} Lemmas 5 and 4, respectively, replacing de Jong's
implicit use of inequalities with explicit inequalities. The
supplemental appendix presents a proof of~\eqref{eq:33} to show the
basic idea.

@@

% LocalWords:  CLT Kun LiS PoR GoW GoJ nt indices eq studentized JoD reindex nj
% LocalWords:  de Jong's ns Mcl AllRefs nn th nm ni HaH formulae jn gcalhoun nN
% LocalWords:  jel PaP DPP np Ames Resampling nonstationary cdf Helle

>>>>

\documentclass[11pt]{article}
\IfFileExists{VERSION.tex}{\input{VERSION}}%
{\date{Pdf compiled \today. (Version unclear; run `make VERSION.tex'.)}}
\input{preamble}
\input{VERSION}
\begin{document}

\author{Gray Calhoun\thanks{Economics Department, Iowa State
    University, Ames, IA 50011. Telephone: (515) 294-6271.  Email:
    \protect\url{gcalhoun@iastate.edu}. Web:
    \protect\url{http://gray.clhn.org}.  I would like to thank
    Helle Bunzel, Dimitris Politis, Robert Taylor, and three anonymous
    referees for their comments and feedback on earlier versions of
    this paper.}}

@@

\begin{abstract}\noindent
  This paper weakens the size and moment conditions needed for typical
  block bootstrap methods (i.e.\ the Moving Blocks, Circular Blocks,
  and Stationary Bootstraps) to be valid for the sample mean of
  Near-Epoch-Dependent (\ned) functions of mixing processes; they are
  consistent under the weakest conditions that ensure the original
  \ned\ process obeys a Central Limit Theorem \citep[those
    of][\textit{Econometric Theory}]{Jon:97}.  In doing so, this paper
  extends De Jong's method of proof, a blocking argument, to hold with
  random and unequal block lengths.  This paper also proves that
  bootstrapped partial sums satisfy a Functional \clt\ under the same
  conditions.

@@

As mentioned earlier, these are the same size and mixing conditions
used by \citet{Jon:97}.
Note that De Jong does allow a little bit more flexibility in the
conditions on the array $\{c_{nt}\}$ \citep[see also][]{Dav:93};
essentially, he allows for a single set of blocks with the
maximal $\{c_{nt}\}$ over each block well-behaved, while this
paper requires this condition to hold for every possible partition of
blocks.  This additional restriction is required because the
Stationary Bootstrap will select the blocks randomly and is similar to
\citepos{JoD:00b} requirement for the \fclt. Similarly, our assumption
on the dispersion of the individual means, $(\mu_{nt} - \bar\mu_n)^2$, is
slightly stronger than \citepos{GoW:02} and \citepos{GoJ:03} to
accommodate larger block sizes.

@@

Results~\eqref{eq:32} and~\eqref{eq:33} are direct extensions of
\citepos{Jon:97} Lemmas 5 and 4, respectively, replacing De Jong's
implicit use of inequalities with explicit inequalities. The
supplemental appendix presents a proof of~\eqref{eq:33} to show the
basic idea.

@@

% LocalWords:  CLT Kun LiS PoR GoW GoJ nt indices eq studentized JoD reindex nj
% LocalWords:  De Jong's ns Mcl AllRefs nn th nm ni HaH formulae jn gcalhoun nN
% LocalWords:  jel PaP DPP np Ames Resampling nonstationary cdf Helle
